---
title: ""
execute: 
  echo: FALSE
---

```{r}
#| label: setup
#| message: FALSE
#| warning: FALSE

library(tidyverse)
library(gtsummary)
library(brms)
library(tidybayes)
library(primer.data)
fit_elec_2020 <- read_rds("fit_elec_2020.rds")
```


```{r}
#| warning: FALSE
#| label: plot
 

# Making my ndata tibble
region <- c("Midwest", "Northeast", "South", "West")

ndata <- expand_grid(region)

# Code for the plot
fit_elec_2020 |>
  add_epred_draws(newdata = ndata) |>
  select(region, .category, .epred) |>
  ggplot(aes(x = .epred, y = .category)) +
    stat_slab(aes(fill = region),
              alpha = 0.5,
              position = "dodge") +
  labs(title = "Election Results by Region (2020)",
       subtitle = "Biden seems to win over every region.",
       fill = "Region",
       y = "Candidate",
       x = "Probability") +
  scale_x_continuous(labels = scales::percent) + 
  theme_minimal()
```

Did voters in the 2020 United States Presidential Election display different beliefs based on their geographical region? Using data from the American National Election Studies (ANES), I seek to predict the relationship between voting behavior and geographical region during the 2020 United States Presidential Election. I modeled region, a factor variable as a logistic regression model of candidate. Individuals across the United States seemed to favor Joe Biden altogether despite their region. Given that a voter is from the South, there is a 51% chance that they will vote for Biden, although that number could be anywhere from 47% to 55%.


